Some Fancy Title

### 2023-09-13 output/paper/manuscript.tex
Tried pre-release of Quarto 1.4 to fix issue with cross-ref of tables but it fails to render PDF. Went back to stable release.

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, enhanced, boxrule=0pt, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

\textbf{?@tbl-chem-info}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, boxrule=0pt, sharp corners]}{\end{tcolorbox}}\fi

@@
